%\documentclass[12pt,preprint]{aastex}
\documentclass[iop,apj,appendixfloats]{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{float}
\usepackage{gensymb}
\usepackage{afterpage}

\usepackage{chngcntr}

%%%%%%%%%%%%%%%%%%%% Definitions
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}

%%\def\wid{width=\linewidth}
\def\Msol{\ensuremath{M_{\odot}}}

\def\abt{$\sim$}

\def\shen{Shen EOS}
\def\ls{LSEOS}

\def\background{$\bar\nu_e + \nu_x$ background}
\def\backgrounds{$\bar\nu_e + \nu_x$ backgrounds}


\def\cer{Cherenkov}

\def\lmax{$L^n_{\nu_e,\mathrm{max}}$}
\def\tmax{$t_{\mathrm{max}}$}
\def\trise{$t_{\mathrm{rise},\nobreak 1/2}$}
\def\tfall{$t_{\mathrm{fall},\nobreak 1/2}$}


\def\ar40{$^{40}$Ar}
\def\nue{$\nu_e$}
\def\anue{$\bar\nu_e$}
\def\nux{$\nu_x$}
\def\nuxpart{$\nu_{\mu,\nobreak \tau}$}
\def\nuxanti{$\bar\nu_{\mu,\nobreak \tau}$}

\def\prd{Phys. Rev. D} 

\def\jcap{J. Cosmology Astropart. Phys.}
                % Journal of Cosmology and Astroparticle Physics




\begin{document}

\title{Detecting the Supernova Breakout Burst in 
Terrestrial Neutrino Detectors}

\author{Joshua Wallace\footnote{joshuajw@astro.princeton.edu}, Adam Burrows}
%\email{joshuajw@astro.princeton.edu}
\affil{Department of Astrophysical Sciences, Princeton
  University, Princeton, NJ 08544, USA}

\and

\author{Joshua C. Dolence}
\affil{Computational Physics Group (CCS-2), MS-K784, Los
  Alamos National Laboratory, P.O. Box 1663, Los Alamos, NM 87545,
  USA}

\begin{abstract}
\input{abstract.tex}
\end{abstract}

\keywords{supernovae: general ---  neutrinos}

\section{Introduction}
\input{intro.tex}

\section{The Supernova Models}
\label{sec:model}
\input{models.tex}


\section{Signal Evolution}
\label{sec:signalevolution}
\input{signals.tex}

\section{Terrestrial Neutrino Detectors}
\label{sec:detection}
\input{detection.tex}


\section{Method}
\label{sec:method}
\input{method.tex}

\section{Results}
\label{sec:discussion}
\input{results.tex}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion.tex}

\acknowledgments

We thank Kate Scholberg, Andr\'e Rubbia, Masayuki Nakahata, and 
Lutz K\"opke
for useful conversations.
We also thank Gabriel Martinez-Pinedo for providing us with tables
for the \ar40\ cross sections.
The authors acknowledge support provided by the NSF PetaApps 
program, under award OCI-0905046 via a subaward no. 44592 from 
Louisiana State University to Princeton University, and by the 
Max-Planck/Princeton Center (MPPC) for Plasma Physics 
(NSF PHY-1144374). The authors employed computational resources 
provided by the TIGRESS high-performance computer center at 
Princeton University, which is jointly supported by the Princeton 
Institute for Computational Science and Engineering (PICSciE) and 
the Princeton University Office of Information Technology and by 
the National Energy Research Scientific Computing Center (NERSC), 
which is supported by the Office of Science of the US Department 
of Energy under contract DE-AC03-76SF00098. This work is part of 
the ``Three Dimensional Modeling of Core-Collapse Supernovae" PRAC 
allocation support by the National Science Foundation (award number 
ACI-1440032). In addition, this research is part of the Blue Waters 
sustained-petascale computing project, which is supported by the 
National Science Foundation (awards OCI-0725070 and ACI-1238993) 
and the state of Illinois. Blue Waters is a joint effort of the 
University of Illinois at Urbana-Champaign and its National Center 
for Supercomputing Applications.


\bibliographystyle{apj}
\bibliography{bibliography}

\begin{appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\theequation}{A\arabic{equation}}
\input{cs.tex}
\end{appendix}

\input{figures.tex}

\end{document}
